\documentclass[a4paper,12pt]{article}
\usepackage{TLCresume}
\usepackage{hyperref}
\begin{document}

%using zitemize instead of itemize will allow for tighter spacing before and after each line

%====================
% EXPERIENCE A
%====================

\vspace*{10pt}
\subsection{{ DJI Technology Co., Ltd. }\hfill Jun. 2022 - Nov. 2022}
\subtext{Test Development Engineer (Internship)}
\begin{zitemize}
\item Data Visualization: Built a Qt application interacting with Drones through ADB (Android Debug Bridg) that could collect, analyze and visualize data from Drones. Developed a visualization analyzer that collect 2.4Ghz, 5.2Ghz and 5.8Ghz freq scan data from Drones and visualize them in real time. Using parralel computing to speed up the data processing and visualization. Profiling the existing system and optimizing the performance of the application.
\end{zitemize}

%==================== 
% EXPERIENCE B 
%==================== 
\vspace*{6pt}
\subsection{{Deemos Technologies Inc.}\hfill Nov. 2022 - Present}
\subtext{Software Engineer(Internship)}
\begin{zitemize}
\item Built a high precision color correction system for high accuracy and resolution 3D scanning images.
\item Built an AI model to synthesis 3D models texture from 2D images based on Nvidia StyleGAN2 and Pix2PixHD.
\item Built a real-time 3D interactive avatar system demo based on audio driven facial expression technologies.
\end{zitemize}

%==================== 
% EXPERIENCE C
%==================== 
\vspace*{6pt}
\subsection{{GeekPie Association}\hfill Sep. 2021 - Present}
\subtext{President of GeekPie Association}
\begin{zitemize}
\item Built a web application for helping every student in ShanghaiTech to choose their courses. Visit \href{https://coursebench.geekpie.club}{coursebench.geekpie.club} to check it out.
\item Built G22G (also known as GeekPie 2022 Game) frontend. Visit \href{https://g22g.geekpie.club}{g22g.geekpie.club} to check it out.
\item Built the homepage of FolST2021 conference (Frontier of Life Science and Technology ShanghaiTech University). You can visit \href{https://clarivy.github.io}{FolST2021} to find the demo.
\end{zitemize}


%==================== 
% EXPERIENCE D
%==================== 
\vspace*{6pt}
\subsection{{Office of Environment Health and Safety, ShanghaiTech University}\hfill Sep. 2021 - Sep. 2022}
\subtext{Assistant Manager}
\begin{zitemize}
\item Built a web application for MSDS information searching and management.
\item Maintained the website of EHS training system. Visit \href{http://www.techkarma.top/elearning-web/index.html}{elearning} to check it out.
\end{zitemize}


\end{document}
